### 2020-11-17 thesis/appendix_1.tex
fix appendices names
fix sectionning
remove suprefluous text

\chapter*{\textbf{Chapter I Supplementary Material \\ \hspace{1em}}}
\addcontentsline{toc}{chapter}{Chapter I Supplementary Material}

@@

\chapter*{\textbf{Chapter II Supplementary Material \\ \hspace{1em}}}
\addcontentsline{toc}{chapter}{Chapter II Supplementary Material}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_45_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end in 2100 (under baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_48_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end in 2100 (under baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_51_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end in 2100 (under baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRefT_compare}
\end{figure}

>>>>

\chapter*{\textbf{Appendix 1: Chapters Supplementary Material \\ \hspace{1em}}}
\addcontentsline{toc}{chapter}{Appendix 1: Chapters Supplementary Material}
\addcontentsline{toc}{section}{Chapter I Supplementary Material}

@@

\chapter*{\textbf{Chapter II Supplementary Material \\ \hspace{1em}}}
\addcontentsline{toc}{section}{Chapter II Supplementary Material}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_45_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end in 2100 (baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_48_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end in 2100 (baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_51_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end in 2100 (baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRefT_compare}
\end{figure}
